\documentclass[12pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{banking} % Style: banking, casual, classic, oldstyle, etc.
\moderncvcolor{green}    % Color: blue, green, orange, red, etc.

% Adjust the page margins
\usepackage[scale=0.85]{geometry}
\usepackage{url} % To handle URLs

% Personal data
\name{Gijo}{Varughese Mathew}
\title{Senior Software Engineer} % Title placed below the name
\address{Bangalore, Karnataka, India}{}{} % Optional
\phone[mobile]{+91 9480921384}
\email{gijovarughese@gmail.com}
\social[linkedin]{linkedin.com/in/gijo-mathew}
\social[github]{github.com/gijocode}
\extrainfo{Python | Web Development | Flask/FastAPI | Bash} % Optional

% Begin the document
\begin{document}

% Print the header with personal information
\makecvtitle

% Section: About Me
\section{About Me}
I’m a results driven backend developer with over 5 years of experience in Python, web development, and cloud-based solutions. I specialize in building efficient systems, automating processes, and integrating enterprise-level functionalities. My problem solving skills and ability to work seamlessly across teams have consistently delivered high-quality results.

% Section: Work Experience
\section{Work Experience}
\cventry{07/2019--Present}{Senior Software Engineer}{Mphasis}{Bangalore, India}{}{
\begin{itemize}
    \item \textbf{Core Developer for HPE OneView for VMware vCenter}: Actively contributed to the integration and development of HPE OneView features within VMware vCenter.
    \item \textbf{Core Developer for HPE Greenlake Compute Ops Manager for VMware vCenter}: Played a key role in incorporating HPE Compute Ops Manager functionalities into VMware vCenter.
    \item \textbf{Core Developer for HPE Compute Ops Manager VMware Integration}: Worked on integrating vLCM (vSphere Lifecycle Manager) capabilities into HPE Compute Ops Manager, improving system management and automation for updates.
    \item Collaborated with management, internal teams, and development partners regarding software application design, status, and project progress.
    \item \textbf{Build and CI/CD Management}: Created, maintained and adapted Jenkins jobs for automating build and deployment processes.
    \item \textbf{Plugin Modernization}: Contributed to porting a legacy plugin to a modern remote plugin architecture.
    \item \textbf{Deployment Automation}: Implemented a fully automated deployment solution, reducing human intervention and saving approximately 90\% of deployment time.
    \item \textbf{Recognitions}: Received multiple Monthly Summit Awards for exceptional performance and contributions.
\end{itemize}}

% Section: Education
\section{Education}
\cventry{08/2015--06/2019}{Bachelor of Engineering in Computer Science}{East Point College of Engineering and Technology}{Bangalore, India}{}{
\begin{itemize}
    \item Grade: 7.3 CGPA
    \item Final Year Project: Gesture-Based Virtual Keyboard using Machine Learning.
    \item Internship: Research Associate at Xcelerator.
\end{itemize}}
\cventry{01/2001--06/2015}{Schooling}{St Vincent Pallotti School}{Bangalore, India}{}{
\begin{itemize}
    \item XII (ISC): 78\%
    \item X (ICSE): 88\%
\end{itemize}}

% Section: Skills
\section{Skills}
\cvitem{Programming}{Python, JavaScript, Shell Scripting, HTML, CSS}
\cvitem{Frameworks}{Flask, FastAPI, jQuery}
\cvitem{Tools}{Git, Jenkins, Docker, Vim, Visual Studio Code}

% Section: Achievements
\section{Achievements}
\cvitem{Hackathon Winner}{Won the Smart India Village Hackathon 2018 in the healthcare domain.}
\cvitem{Competitive Programming}{First place in Java Master 2017, a college-level programming challenge.}

% Section: Projects
\section{Projects}
\cvitem{Live Cricket Score App}{A Python-based macOS app that displays live cricket scores. \newline\hspace*{1em}\url{https://github.com/gijocode/CricketLiveScoreforMacOS}}
\cvitem{PDF Utility Toolbox}{A tool for merging, splitting, and unlocking PDFs. \newline\hspace*{1em}\url{https://github.com/gijocode/PDFUtils}}
\cvitem{The Movie Showcase}{A Python app to retrieve IMDb data and process torrent files. \newline\hspace*{1em}\url{https://github.com/gijocode/MovieVault}}
\cvitem{YouTube-Spotify Sync}{Syncs playlists between YouTube and Spotify using APIs. \newline\hspace*{1em}\url{https://github.com/gijocode/Youtube-Spotify-Sync}}
\cvitem{Church PPT Utility}{Simplifies creating PowerPoint presentations for church events. \newline\hspace*{1em}\url{https://github.com/gijocode/Church-PPT-Utility}}

\end{document}
